Homicide Increases in the COVID-19 Era

### 2025-02-27 Draft1.qmd
Added Boxplot
updated code

covid_la <- covid_14day %>% filter(grepl("Los Angeles", geo_merge))
covid_la$area <- gsub("Los Angeles - ", "", covid_la$geo_merge)

@@

crime_by_area <- crime_by_area %>% left_join(bureaus, join_by("AREA.NAME" == "Division"))
```

@@

# covid data
covid_la$date <- ymd(covid_la$ep_date)
covid_la$month <- month(covid_la$date)
covid_la$year <- year(covid_la$date)
covid_la$date <- day(covid_la$date)
# since there is a 7 day lag in reporting, let's do monthly = cases on the 21st and on the 5th of the next month.
covid_la$lagged <- covid_la$date + 7

covid_la_lagged <- covid_la %>% filter(lagged %in% c(21, 35)) %>% arrange(month, year)

>>>>

@@

crime_by_area <- crime_by_area %>% left_join(bureaus, join_by("AREA.NAME" == "Division"))

ggplot(crime_by_area, aes(y = numberOfCrimes, group = Bureau, x = Bureau)) + 
        geom_boxplot(aes(fill = Bureau))
```

@@

# covid data
covid_14day$date <- ymd(covid_la$ep_date)
covid_14day$month <- month(covid_la$date)
covid_14day$year <- year(covid_la$date)
covid_14day$date <- day(covid_la$date)
# since there is a 7 day lag in reporting, let's do monthly = cases on the 21st and on the 5th of the next month.
covid_14day$lagged <- covid_la$date + 7

covid_la_lagged <- covid_14day %>% filter(lagged %in% c(21, 35)) %>% arrange(month, year)
